---
title: "COVID-19 Situation"
output: github_document
fig_width: 15
fig_height: 8
---

*Plots:*
```{r echo=FALSE,warning=FALSE,include=FALSE}
source("setup/pipe1.R")
source("Descriptive Plots/MainPlots.R")
```


```{r echo=FALSE,fig.width= 10, fig.height=5,warning=FALSE}

t(0) %>% ggplot(mapping = aes(x = Longitude, y = Latitude)) +
  geom_point(mapping = aes(size = Confirmed),alpha = 1.5,color = "red") +
  labs(title = "Spatial Map of Number of Cases Depicted as Point Size")

inUS

theCurve

comparison

comparison2

inWI

onEarth

notInChina

inChina

inItaly

inIran

```
____
*US Rates:*
```{r echo=FALSE}
# source("US.R")
# 
# USrates <- c()
# for(i in 1:(nrow(c$US)-1)){
#   USrates[i] <- (c$US$confirms[i+1]/c$US$confirms[i])
# }
# 
# 
# nifty50 %>% ggplot(mapping = aes(x = day, color = `Rate Type`)) +
#   facet_wrap(~state) +
#   geom_line(mapping = aes(y = value))
# 
# 
# print(str_c("The average rate of growth in the US since 1-22-2020 is a ",(mean(USrates) - 1)," percent increase in confirmed cases daily"))
```

  *If it is increasing by 0% then this means there were no new cases in that day. In terms of exponential growth as this constant goes from  > 0  to  < 0 this could mean that the rate of increase in cases is decreasing and there is no longer exponential growth. Examining this rate in recent chunks allows us to gauge what the current situation is in terms of how it is growing. Any positive number means continued exponential growth. But if it is 0 or less it could mean that transmission will start to taper out.*

